A novel 1000\,\,MW double-reheat ultra supercritical system with turbine-extraction-heated air preheaters and low temperature economizers

### 2018-01-26 article.tex
修改到系统分析部分，接下来分析空预器 对分析部分进行修改1把系统间部件用损失对比从损失百分比换成损失量2把抽汽对比换成表、 对分析部分思路是：分析抽汽变化后分析空预系统和回热系统的参数损失变化 1空预系统和原系统的总损失和效率进行对比，指出最后一级空预器效率低的原因，并贴出烟温对比图 回热系统 2回热系统采用累计柱状图对其进行对，指出总用损失变化不大但是部分用损失有区别

\begin{table}[htbp]
\caption{The main input parameter of reference system }
\label{tab:ref input}
\centering
\begin{tabular}{lll}
\toprule 
Items & Unit & Value\tabularnewline
\midrule
 Live steam mass flow rate 	    	&t/h 			&2533 \\
 Live steam pressure 		    	&bar 			&310\\
 Live steam temperature		     	&$^\circ$C		&600		\\
 First reheat steam pressure    	&bar			&100.9		\\
 First reheat steam temperature  	&$^\circ$C		&610		\\
 Second reheat steam pressure    	&bar			&30.8		\\
 Second reheat steam temperature 	&$^\circ$C		&610		\\
 Power generation output 			&MW				&1000		\\
\bottomrule
\end{tabular}	
\end{table}
Table 2 gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 25$^\circ$C, leading to the exergy loss of 27.17\,MW. The temperature difference of the air preheater is calculated to be 72$^\circ$C, and average temperature of the air is 177$^\circ$C, causing the exergy efficiency of 77.16\%.
\begin{table}[htbp]
\caption{fluid parameters of heat exchangers and air preheater}
\label{tab:reheater parameter}
\centering
\begin{tabular}{llll}
\toprule 
\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{2.7cm}{Cold fluid temperature($^\circ$C)}&  \multirow{2}{2.5cm}{LMTD($^\circ$C)}\tabularnewline
&&&\tabularnewline
\midrule
APH  &  376.00 	& 23.00  & 72.4\tabularnewline
AOC1 &   526.56 & 304.51 & 69.75\tabularnewline
AOC2 &  527.48 	& 304.51 & 60.81\tabularnewline
HRH1 &   417.07 & 273.62 & 10.64\tabularnewline
HRH2 &   314.53 & 240.73 & 10.77\tabularnewline
HRH3 &   434.54 & 205.89 & 12.68\tabularnewline
HRH4 &   316.51 & 186.48 & 6.88\tabularnewline
LRH6 &  394.01 	& 140.46 & 13.19\tabularnewline
LRH7 &   313.17 & 104.49 & 15.87\tabularnewline
LRH8 &   191.84 & 82.42  & 9.82\tabularnewline
LRH9 &   116.61 & 59.25  & 10.03\tabularnewline
\bottomrule
\end{tabular}
\end{table}

@@

\subsection{Thermodynamic performance evaluation} % (fold)
\label{sub:Thermodynamic_evaluation}
Based on the analysis of the reference system, the temperature difference of the heat exchangers is very high and exergy efficiency is rather low. Using turbine extractions to heat air can realize the reduce the heat transfer temperature difference and improve efficiency. The economizer outlet flue gas is used to heat low-temperature economizer can also reduce the loss of regenerative system.
% In order to complete the heat balance calculation of the thermodynamic system, the key parameters in the novel system need to be set.
% The novel system’s parameters are based on reference system, so the main parameters must be the same. The main parameters settled are including: superheat steam’s mass flow, pressure and temperature; First/second reheater’s inlet and outlet pressure and temperature; Turbine Exhaust pressure and temperature; turbine extraction’s pressure and temperature/ specific enthalpy etc. The main parameters settled under THA situation can be found in Table 1 and Table 4 . 
The results of exergy analysis of the optimization system are presented in Table 5. It is found that the optimization system has an improvement in exergetic performance. The total exergy loss of the cascaded utilization system is 1096.52 MW, which is 32.28 MW lower than the original. The new system also brings the improvement from 46.98\% to 47.99\%. Results show that the exergy loss of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%. In addition, there is almost no change of the exergy parameters of the steam turbines, generator and condenser. For the air heating system and regenerative system, great change happens compared with the formal system, and detailed analysis will be carried out next.

\begin{table}
\caption{Thermodynamic performance of the reference and novel systems}
\label{table:thermal performance compare}
\centering
\begin{tabular}{p{7.5cm}p{1.75cm}p{1.75cm}}
\toprule 
Items & Reference system & Novel system\tabularnewline
\midrule
Net generating power (MW) & 999.10 & 1011.19\tabularnewline
Generating efficiency (\%) & 47.69 & 48.73\tabularnewline
Addition in generating efficiency (\%) &  & 1.04\tabularnewline
Standard coal consumption rate (g/kWh) & 257.59 & 252.10\tabularnewline
Reduction in standard coal consumption rate (g/kWh) &  & 5.49\tabularnewline
Exergy efficiency (\%) & 46.51 & 47.52\tabularnewline
Addition in generating efficiency (\%) &  & 1.01\tabularnewline
\bottomrule
\end{tabular}
\end{table}

% subsubsection subsubsection_name (end)

>>>>

\begin{table}[htbp]
\caption{The main input parameter of reference system }
\label{tab:ref input}
\centering
\begin{tabular}{lll}
\toprule 
Items & Unit & Value\tabularnewline
\midrule
 Live steam mass flow rate 	    	&t/h 			&2533 \\
 Live steam pressure 		    	&bar 			&310\\
 Live steam temperature		     	&$^\circ$C		&600		\\
 First reheat steam pressure    	&bar			&100.9		\\
 First reheat steam temperature  	&$^\circ$C		&610		\\
 Second reheat steam pressure    	&bar			&30.8		\\
 Second reheat steam temperature 	&$^\circ$C		&610		\\
 Power generation output 			&MW				&1000		\\
\bottomrule
\end{tabular}	
\end{table}
Table 2 gives the temperature profiles and exergy efficiency of regenerative heaters and the air preheater, revealing the energy match level of heat exchangers.
For the air preheater, the temperature of flue gas at the inlet of the air preheater is 376$^\circ$C under THA condition, while the temperature of the air to be heated by the flue is 25$^\circ$C, leading to the exergy loss of 27.17\,MW. The temperature difference of the air preheater is calculated to be 72$^\circ$C, and average temperature of the air is 177$^\circ$C, causing the exergy efficiency of 77.16\%.
\begin{table}[htbp]
\caption{fluid parameters of heat exchangers and air preheater}
\label{tab:reheater parameter}
\centering
\begin{tabular}{llll}
\toprule 
\multirow{2}{2cm}{Components} &\multirow{2}{2.7cm}{Hot fluid temperature($^\circ$C)}  & \multirow{2}{3.2cm}{Cold fluid temperature ($^\circ$C)}&\multirow{2}{2.5cm}{LMTD ($^\circ$C)}\tabularnewline
&&&\tabularnewline
\midrule
APH  &  376.00 	& 23.00  & 72.4\tabularnewline
AOC1 &   526.56 & 304.51 & 69.75\tabularnewline
AOC2 &  527.48 	& 304.51 & 60.81\tabularnewline
HRH1 &   417.07 & 273.62 & 10.64\tabularnewline
HRH2 &   314.53 & 240.73 & 10.77\tabularnewline
HRH3 &   434.54 & 205.89 & 12.68\tabularnewline
HRH4 &   316.51 & 186.48 & 6.88\tabularnewline
LRH6 &  394.01 	& 140.46 & 13.19\tabularnewline
LRH7 &   313.17 & 104.49 & 15.87\tabularnewline
LRH8 &   191.84 & 82.42  & 9.82\tabularnewline
LRH9 &   116.61 & 59.25  & 10.03\tabularnewline
\bottomrule
\end{tabular}
\end{table}

@@

\subsection{Thermodynamic performance evaluation} % (fold)
\label{sub:Thermodynamic_evaluation}
Based on the analysis of the reference system, the temperature difference of the heat exchangers is very high and exergy efficiency is rather low.
Using turbine extractions to heat air can realize the reduce the heat transfer temperature difference and improve efficiency. 
The economizer outlet flue gas is used to heat low-temperature economizer can also reduce the loss of regenerative system.
% In order to complete the heat balance calculation of the thermodynamic system, the key parameters in the novel system need to be set.
% The novel system’s parameters are based on reference system, so the main parameters must be the same. The main parameters settled are including: superheat steam’s mass flow, pressure and temperature; First/second reheater’s inlet and outlet pressure and temperature; Turbine Exhaust pressure and temperature; turbine extraction’s pressure and temperature/ specific enthalpy etc. The main parameters settled under THA situation can be found in Table 1 and Table 4 . 
% 对于新旧系统表格的热力参数进行分析，下面这段话太少

\begin{table}
\caption{Thermodynamic performance of the reference and novel systems}
\label{table:thermal performance compare}
\centering
\begin{tabular}{p{7.5cm}p{1.75cm}p{1.75cm}}
\toprule 
Items & Reference system & Novel system\tabularnewline
\midrule
Net generating power (MW) & 999.10 & 1011.19\tabularnewline
Generating efficiency (\%) & 47.69 & 48.73\tabularnewline
Addition in generating efficiency (\%) &  & 1.04\tabularnewline
Standard coal consumption rate (g/kWh) & 257.59 & 252.10\tabularnewline
Reduction in standard coal consumption rate (g/kWh) &  & 5.49\tabularnewline
Exergy efficiency (\%) & 46.51 & 47.52\tabularnewline
Addition in generating efficiency (\%) &  & 1.01\tabularnewline
\bottomrule
\end{tabular}
\end{table}
% 根据用损失对比表从新进行分析，从为什么锅炉空预器效率提高，其他不变或者降低说起
The results of exergy analysis of the optimization system are presented in Table~\ref{table:system exergy campare}. 
It is found that the optimization system has an improvement in exergetic performance.
 The total exergy loss of the cascaded utilization system is 1096.52 MW, which is 32.28 MW lower than the original. 
 The new system also brings the improvement from 46.98\% to 47.99\%. 
 Results show that the exergy loss of boiler is 855.72 MW, leading to the increment of exergy efficiency by 0.18\%. In addition, there is almost no change of the exergy parameters of the steam turbines, generator and condenser. 
 For the air heating system and regenerative system, great change happens compared with the formal system, and detailed analysis will be carried out next.

\begin{table}
\caption{Systems' exergy destruction rate comparison }
\label{table:system exergy campare}
\centering
\begin{tabular}{lll}
\toprule 
Items & Reference System\,(MW) & Novel System\,(MW)\tabularnewline
\midrule 
Boiler(without AP) & 883.26 & 872.22\tabularnewline
Turbine & 63.33 & 63.97\tabularnewline
Air Preheater  & 27.39 & 16.55\tabularnewline
Regenerative system & 22.53 & 21.56\tabularnewline
Other & 131.03 & 142.42 \tabularnewline
Total & 1116.72 & 1127.54\tabularnewline
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\label{table:extraction compare}
\caption{Systems' extractions comparison}
\begin{centering}
\begin{tabular}{llll}
\toprule 
\multirow{2}{*}{Extractions} & \multirow{2}{2.5cm}{Reference system (kg/s)} & \multicolumn{2}{c}{Novel system (kg/s)}\tabularnewline
\cmidrule{3-4} 
 &  & to RHs & to APHs\tabularnewline
\midrule
1st & 54.47 & 43.79 & 15.42\tabularnewline
2nd & 52.18 & 18.52 & 13.5\tabularnewline
3rd & 37.86 & 31.71 & 14.62\tabularnewline
4th & 20.53 & 5.66 & 9.5\tabularnewline
5th & 11.95 & 9.78 & 5.67\tabularnewline
6th & 19.94 & 9.88 & 7.83\tabularnewline
7th & 30.19 & 14.16 & 12.85\tabularnewline
8th & 16.31 & 3.11 & 27.1\tabularnewline
9th & 18.93 & 18.93 & 0\tabularnewline
10th & 20.61 & 20.6 & 0\tabularnewline
Total & 282.97 & 176.14 & 106.49\tabularnewline
\bottomrule
\end{tabular}
\par\end{centering}
\end{table}
% subsubsection subsubsection_name (end)
